Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-29 doc/gaia-chapter.tex
more snippets in gaia-chapter
fix typos
untangling gaia's proof of well-foundedness of the order on T1

@@

\inputsnippets{nfwfgaia/nfWfProofa}

The following elimination on \texttt{a} pushes a new hypothesis \texttt{Hb} which --- in the same terms as in Section~\vref{sec:strongly-accessible} --- tells that any ordinal less than $a$ is ``strongly accessible''.

\inputsnippets{nfwfgaia/nfWfProofb, nfwfgaia/nfWfProofc}

@@

There are three cases to consider:
\begin{itemize}
\item It is of the form \texttt{(cons a' n' b')} where \texttt{a'} is strictly less than \texttt{a}. Then, it is accessible (by hypothesis \texttt{Hb}).
  \inputsnippets{nfwfgaia/nfWfProofd}

\end{itemize}

>>>>

This proof, as it appears in \href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}, is quite dense and qualified as ``a bit tricky''. We present here its main steps with the help of the alectryon tool.

@@

\inputsnippets{nfwfgaia/nfWfProofa}
We start with classic structural induction on \texttt{a}.

\inputsnippets{nfwfgaia/nfWfProofaa}
The following \texttt{ssreflect} tactic  pushes a new hypothesis \texttt{Hb} which --- in the same terms as in Section~\vref{sec:strongly-accessible} --- tells that any ordinal less than $a$ is ``strongly accessible''.

\inputsnippets{nfwfgaia/nfWfProofb}

@@

There are three cases to consider.
\begin{enumerate}
\item It is of the form \texttt{(cons a' n' b')} where \texttt{a'} is strictly less than \texttt{a}.
  \inputsnippets{nfwfgaia/nfWfProofd}

  Then, it is accessible (by hypothesis \texttt{Hb}).

  \item The considered term  is equal to
    \texttt{(cons a n b'')}, where $b''<\omega^a$. 
    \inputsnippets{nfwfgaia/nfWfProofg}

    Then we can replace \texttt{a''} with \texttt{a}, \texttt{n''} with \texttt{n}, and apply the hypotheses \texttt{Hd} and \texttt{He}.

\item
  The term is equal to
  \texttt{(cons a n'' b'')}, where $n''<n$ and $b''<\omega^a$.
  This term is less than the accessible \texttt{(cons a n b'')}.

  \inputsnippets{nfwfgaia/nfWfProofe}

 Then we can apply the hypothesis \texttt{He}.

\end{enumerate}

In every case, the considered ordinal is accessible.
